---
title: "Algoritma KNN"
author: "Rani Ayu Sukmawati-Institut Teknologi Statistika dan Bisnis Muhammadiyah"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    higlight: zenburn
    toc: true
    toc_float:
      collapsed: true
    df_print: paged
bibliography: references.bib
---

```{=html}
<style>
body{
text-align: justify}
</style>
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Algoritma KNN
Algoritma Nearest Neighbor Retrieval (K-Nearest Neighbor atau K-NN) adalah
sebuah algoritma untuk melakukan klasifikasi terhadap objek dengan data pembelajaran yang jaraknya paling dekat dengan objek tersebut. Kasus khusus di mana
klasifikasi diprediksikan berdasarkan data pembelajaran yang paling dekat (dengan
kata lain, k = 1) disebut algoritma Nearest Neighbor.

# Tahapan Algoritma KNN
1. Menyiapkan Dataset
2. Mengubah dataset menjadi training dan testing
3. sebelum pemprosesan
4. training dan train control

# Eksperimen Algoritma KNN

## Library

1.Menyiapkan data
```{r}
library(caret)
```

```{r}
summary(iris)
```

2.Membagi dataset menjadi training dan testing
```{r}
set.seed(300)
#Spliting data as training and test set. Using createDataPartition() function from caret. p is the percentage of data that goes to training. 
indxTrain <- createDataPartition(y = iris$Species,p = 0.75,list = FALSE)
training <- iris[indxTrain,]
testing <- iris[-indxTrain,]

#Checking distibution in original data and partitioned data
```

```{r}
prop.table(table(testing$Species)) * 100
```

```{r}
prop.table(table(iris$Species)) * 100
```

3. Sebelum pemprosesan
```{r}
trainX <- training[,names(training) != "Species"]
preProcValues <- preProcess(x = trainX,method = c("center", "scale"))
preProcValues
```

4.Training dan train control
```{r}
set.seed(400)
ctrl <- trainControl(method="repeatedcv",repeats = 3) #,classProbs=TRUE,summaryFunction = twoClassSummary)
knnFit <- train(Species ~ ., data = training, method = "knn", trControl = ctrl, preProcess = c("center","scale"), tuneLength = 20)
#Output of kNN fit
knnFit
```

```{r}
#Plotting yields Number of Neighbours Vs accuracy (based on repeated cross validation)
plot(knnFit)
```

```{r}
knnPredict <- predict(knnFit,newdata = testing )
#Get the confusion matrix to see accuracy value and other parameter values
confusionMatrix(knnPredict, testing$Species )
```

```{r}
mean(knnPredict == testing$Species)
```

# Referensi
https://rpubs.com/arikunc0r0/kNNwithCaret